gij bent 2

### 2025-09-28 paper/paper.qmd
Remove uppercase in Julie graph legend

# Plot
ggplot(df, aes(x = time)) +
  geom_line(aes(y = s_curve, colour = "S-curve (Cumulative Adoption)"), linewidth = 1) +
  geom_line(aes(y = bell_curve, colour = "Bell Curve (Adoption Rate)"), linewidth = 1, linetype = "dashed") +
  geom_vline(data = cuts, aes(xintercept = x, colour = label), linetype = "dashed") +
  scale_colour_manual(
    name = "Legend",
    values = c("S-curve (Cumulative Adoption)" = "purple",
               "Bell Curve (Adoption Rate)" = "deeppink",
               "Innovators" = "red",
               "Early Adopters" = "orange",
               "Early Majority" = "goldenrod3",
               "Late Majority" = "darkgreen",
               "Laggards" = "blue")
  ) +
  labs(
    title = "S-curve and bell curve",
    x = "Time step",
    y = "Adoption percentage"
  ) +
  theme_minimal(base_size = 14)

>>>>

# Plot
ggplot(df, aes(x = time)) +
  geom_line(aes(y = s_curve, colour = "S-curve (Cumulative Adoption)"), linewidth = 1) +
  geom_line(aes(y = bell_curve, colour = "Bell Curve (Adoption Rate)"), linewidth = 1, linetype = "dashed") +
  geom_vline(data = cuts, aes(xintercept = x, colour = label), linetype = "dashed") +
  scale_colour_manual(
    name = "Legend",
    values = c("S-curve (cumulative adoption)" = "purple",
               "Bell curve (adoption Rate)" = "deeppink",
               "Innovators" = "red",
               "Early adopters" = "orange",
               "Early majority" = "goldenrod3",
               "Late majority" = "darkgreen",
               "Laggards" = "blue")
  ) +
  labs(
    title = "S-curve and bell curve",
    x = "Time step",
    y = "Adoption percentage"
  ) +
  theme_minimal(base_size = 14)
